Minimax Rates in Contextual Partial Monitoring

### 2018-09-07 rebuttal.tex

\documentclass{article}

\usepackage{nips_2018_author_response}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\begin{document}
We give thanks to all for spending the effort to understand our submission and for the encouraging feedback!

\textbf{Reviewer 1:}
We could not achieve the $\sqrt{T}$ with a relaxation algorithm. While it is not even known how to do this in the simpler case of bandit feedback, $\sqrt{T}$ would be a good contribution (we have some ideas). We will expand the related works section (especially adding citation about other partial feedback games) and will work on the unclear sections of the proof. Thanks for the specific suggestions; we will make the corrections and have tried to answer your questions below.

\textit{L125:} The matrix L is fixed, but $\ell_i$ is the expected loss under the adversary's empirical distribution and can still be impossible to learn. We'll clarify.
\textit{L129:} to calculate $v_{i,j,k}$, it suffices to find a pseudo inverse of $S$.
Alg1: EXP4 used the estimator described on L123, but the recentering is novel (actually concurrently proposed by [11]).
\textit{L258:} yes, this is a good point.
\textit{L262:} ``all fixed actions'' means that, for every action, we include the policy that always selects that action. A lower bound with just an arbitrary policy class was too weak of a result, as it is easy to make all the policies bad.
%\textit{L271:} rank nullity theorem

\textbf{Reviewer 3:}
Models:
Our intention was not to be coy about the i.i.d. assumption, which is critical (it is first mentioned in the abstract, L13), but we agree that all model assumptions should be very clear, and we will emphasize that the EXP4.PM regret bounds hold for adaptive $x_t$, $j_t$, but the relaxation algorithm requires $x_t$ to be i.i.d. We will clarify in the intro and the section headers.

We completely agree with the reviewer: the interesting questions are how $\Pi$ and $R_T$ interact. We have only taken the coarsest view, either finding bounds in terms of $\log |\Pi|$ or the Rademacher complexity-like term in Corollary 1. Having said that, no paper in the contextual bandit setting has a more refined analysis either. However, the partial monitoring setting is more nuanced than the bandit setting; indeed, if we take $\Pi$ to be the set of constant actions, then $\sqrt{T}$ regret is possible with only local observability, so there is possibly a more subtle boundary for the rates.

Additionally, there are more refined, game-dependent notions of complexity where the uniform distribution over the hypercube in the complexity term is replaced with a uniform distribution over the columns of $H$, and hence the regret will depend on the structure of the feedback through more than a dependence on the number of actions. We omitted these arguments for brevity (and they also require $O(N^2)$ computation), but are working on using them for a more refined bound.

The complexity measure in Corollary 1 is what is needed to be able to prove admissibility of the relaxation, but other cleaner notions may be possible. In the full information setting, sequential Rademacher complexities are needed to handle adversarial contexts, but it is unknown how to extend the relaxation approach to adversarial contexts in both bandits or partial monitoring.

Finally, the $j_t = f(x_t)$ case was studied in [4], but only when $f$ is a linear or logistic function; indeed $\sqrt{T}$ is possible without a pairwise observability condition. We will add this comparison.

\textbf{Reviewer 4:}
We will be more clear about the small algorithmic innovations and the intuition behind them. Providing a clear picture of the lower bound shorter than a few pages was difficult and we opted to describe the construction in detail. The high-level intuition is as follows. In the contextual case, pick arbitrary non-neighboring actions $i$ and $j$; there is a policy class where $i$ and $j$ are essentially neighbors in that determining the optimal policy will require resolving between the loss of $i$ and $j$. Hence, if there exists such a pair, then the algorithm will be forced to play other actions to resolve $\ell_i-\ell_j$, and the $T^{2/3}$ lower bound reasoning applies. We'll add this intuition and streamline the rest.

We will also address the rest of your fixes and tone down the optimality claims. Extra thanks for the correct inequality!

\end{document}

### 2018-09-07 rebuttal.txt

Rebuttal:

We give thanks to all for spending the effort to understand our submission and for the encouraging feedback!

Reviewer 1:
We tried to but could not achieve the sqrt(T) with a relaxation algorithm. It is not even known how to do this in the simpler case of bandit feedback, but we agree that sqrt(T) would be a good contribution (we have some ideas).

We will beef up the related works section (especially adding citation about other partial feedback games such as graph feedback) and will work on the unclear sections of the proof. Thanks for the specifics; we will make the corrections and have tried to answer your questions below.

L125: The matrix L is fixed, but ell_i is the expected loss under the adversary's empirical distribution and can still be impossible to learn. We'll clarify.
129: to calculate v, it suffices to find a pseudo inverse of S
Alg1: EXP4 used the estimator described on L123, but the recentering is novel (actually concurrently proposed by [11])
L258: yes, good point
L262: "all fixed actions" means adding the identity policies to \Pi. A lower bound with just an arbitrary policy class was too weak of a result, as it is easy to make all the policies bad.
L271: rank nullity theorem

Reviewer 3:

Models:
Our intention was not to be coy about the iid assumption, which is critical (it is first mentioned in the abstract, L13), but we agree that all model assumptions should be very clear, an we will emphasize that the exp4.pm regret bounds hold for adaptive x_t, j_t, but the relaxation algorithm requires x_t to be i.i.d. and also needs access to x_t samples. We will clarity in the intro and the section headers.

We completely agree with the reviewer: the interesting questions are how Pi and R_T interact. We have only taken the most coarse view, either finding bounds in terms of log |Pi| or the Rademacher complexity-like term in Corollary 1. In our defense, no paper in the contextual bandit setting has a more refined analysis either.

The complexity measure for Pi is derived by what is needed to be able to prove admissibility of the relaxation, but other cleaner notions may be possible. In the full information setting, sequential Rademacher complexities to handle adversarial contexts. It is unknown how to extend the relaxation approach to adversarial contexts in both bandit or partial monitoring, so the Rademacher-like term is the most natural in this setting. However, the partial monitoring setting is more nuanced than the bandit setting; indeed, if we take Pi to be the set of constant actions, then T^1/2 regret is possible with only local observability, so there is possibly a more subtle boundary for the rates.

Additionally, there are more refined, game-dependent notions of complexity where the uniform distribution over the hypercube in the complexity term is replaced with a uniform distribution over the columns of H, and hence the regret will depend on the structure of the feedback through more than a dependence on the number of actions. We omitted these arguments for brevity, but are working on using them for a more refined bound.

Finally, the j_t = f(x_t) case was studied in [4], but only in the case where f is a linear or logistic function; indeed sqrt(T) is possible without a pairwise observability condition. We will add this comparison.

Reviewer 4:
We will be more clear about the small algorithmic innovations and the intuition behind them. Providing a clear picture of the lower bound shorter than a few pages was difficult and we opted to describe the construction in detail. The high level intuition is as follows. In the contextual case, pick arbitrary non-neighboring actions i and j; there is a policy class there i and j are essentially neighbors in that determining the optimal policy will require resolving between the loss of i and j. Hence, if there exists such a pair, then the algorithm will be forces to play other actions to resolve ell_i-ell_j, and the usual lower bound implies a T^2/3 lower bound. We'll add this intuition and streamline the rest.

We'll also address the rest of your fixes and tone down the optimality claims and add dimensions. Extra thanks for the correct inequality!

### 2018-09-07 pap.tex
bib now works.
fixed the bug, i think.

\newpage
\bibliography{../../big_bib}

@@

  We now check the inductive step. We define $\rho = (x_t,\eepsilon_t,\Z_t)_{t+1:T}$ to the collection of random variables in the relaxation. Recall that our aim is to prove admissibility of the strategy $q_t(\rho) = (1-N\gamma)q_t^*(\rho)+ \gamma \ones$ where $q_t^*(\rho)$ was defined by
  \begin{align*}
  q_t^*(\rho)
  &=
  \argmin_{q \in \triangle_{N}}
  \sup_{p_t \in \triangle_{\mathcal D}'} 
    \exop_{\hat\Delta_t \sim p_t}\left[
    q^\top\hat\Delta_t
    +  \sum_{i=1}^N R_i\left(\hist^{t},\rho\right)
    \right].
\end{align*}
By construction, no entry of $q_t(\rho)$ is below $\gamma$. It is then easy to check that, for $q_t^* = \ex_{\rho}[q_t^*(\rho)]$ and $q_t = \ex_{\rho}[q_t(\rho)]$,
\[
  \ex_{I_t \sim q_t}\left[ \Delta_t ^\top e_{I_t} \right] = \Delta_t^\top q_t  
  \leq \Delta_t^\top q_t^* + N\gamma
  =
  \ex_{I_t\sim q_t} \left[ \hat\Delta_t(I_t,j_t,q_t)^\top q_t^* \right] + N\gamma,
\]
where we have been explicit that $\hat\Delta_t(I_t,j_t,q_t)$ is a random variable that depends on the player actions and the $q_t$ (since $\Z_t$'s distribution is a function of $q_t$).

For every fixed $x_t$, we can apply the above inequality and unpack the definition of the relaxation to find
\begin{align*}
  \sup_{j_t} \mathop{\ex}_{I_t\sim q_t}\left[e_{I_t}^\top\hat\Delta_t(I_t,j_t,q_t)
  +  \rel(\hist^t) \right]
  &=
    \sup_{j_t } \mathop{\ex}_{I_t\sim q_t}\left[e_{I_t}^\top\hat\Delta_t(I_t,j_t,q_t)
    +  \sum_{i=1}^N \exop_\rho\left[R_i\left(\hist^{t},\rho\right)\right]\right]\\
  &\quad + (T-t)N\gamma\\
  &\leq
    \sup_{j_t} \mathop{\ex}_{I_t\sim q_t}\left[(q_t^*)^\top\hat\Delta_t(I_t,j_t,q_t)
    +
  \sum_{i=1}^N\exop_\rho\left[R_i\left(\hist^{t},\rho\right)\right]\right]\\
  &\quad+(T-t+1)N\gamma.
\end{align*}
Defining $A_i(\pi) = -\sum_{s=1}^{t-1} \pi(x_s)^\top D_i \hat \Delta_s - \sum_{s=t+1}^T 2\pi(x_s) \eepsilon_{s,i} \Z_{s}$, the previous line is equal to
\begin{align*}
\lefteqn{\sup_{j_t} \mathop{\ex}_{I_t\sim q_t}\left[(q_t^*)^\top\hat\Delta_t(I_t,j_t,q_t)
    +
  \mathop{\ex}_{\rho}\left[\sum_{i=1}^N \sup_{\pi} - \pi(x_t)^\top \hat\Delta_t(I_t,j_t,q_t) + A_i(\pi)
  \right]\right] + (T-t+1)N\gamma}\\
  &\quad =
    \sup_{j_t} \sum_{i=1}^N\mathop{\ex}_{I_t\sim q_t}\left[\mathop{\ex}_{\rho}\left[ q_t^*(\rho)^\top \hat \Delta_t (I_t,j_t,q_t)
    +
    \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t(I_t,j_t,q_t) + A_i(\pi)\right]\right]\\
  &\quad+ (T-t+1)N\gamma.
\end{align*}

@@

Specifically, every coordinate of $\hat\Delta_t(I_t,j_t,q_t)$  has large probability of being zero: if we fix $q_t$ by conditioning on $\rho$, then
\begin{align*}
  P\left(\hat\Delta_t(I_t,j_t,q_t)^\top e_i = 0 \right)
  &=
    \ex_{\rho}\left[ \ex_{I_t \sim q_t(\rho)}\left[ P\left(\hat\Delta_t(I_t,j_t,q_t)^\top e_i = 0 \middle |\rho, I_t\right)\right]\right]\\
    &=
    \ex_{\rho}\left[ \ex_{I_t \sim q_t(\rho)}\left[
    1-\frac{\gamma \vert e_i^\top V(I_t)^\top Y_t\vert }{V_\infty q_t(\rho)(I_t)}
    \right]\right]\\
  &\geq
    \ex_{\rho}\left[ \ex_{I_t \sim q_t(\rho)}\left[
    1-\frac{\gamma}{q_t(\rho)(I_t)}
    \right]\right]\\
  &= \ex_{\rho}\left[
    \sum_{i=1}^N q_t(\rho)(i) \left(1- \frac{\gamma}{q_t(\rho)(i)}\right)\right]\\
  &= 1 - N \gamma.
\end{align*}
Therefore, the distribution of $\hat\Delta_t(I_t,j_t,q_t)$ is always in $\triangle_{\mathcal D}'$, and we obtain an upper bound by allowing the adversary to play distributions over a random variable named $\hat\Delta_t$ with distribution in $\triangle_{\mathcal D}'$. With this substitution, $I_t$ and $j_t$ no longer appear in the expression. Suppressing the $(T-t+1)N\gamma$ term, we have
\begin{align*}
  &\lefteqn{
        \sup_{j_t } \sum_{i=1}^N\mathop{\ex}_{I_t\sim q_t}\left[\mathop{\ex}_{\rho}\left[ q_t^*(\rho)^\top \hat \Delta_t(I_t,j_t,q_t)
    +
    \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t(I_t,j_t,q_t) + A_i(\pi)\right]\right]
    }\\
  &\leq
    \sup_{p_t\in\triangle_{\mathcal D}'} \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[
    \sum_{i=1}^N\mathop{\ex}_{\rho}\left[ q_t^*(\rho)^\top \hat \Delta_t
    +
    \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right]\right]\\
    &\leq
\mathop{\ex}_{\rho}\left[ \sup_{p_t\in\triangle_{\mathcal D}'}\sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ q_t^*(\rho)^\top \hat \Delta_t
    +
  \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right]\right].
\end{align*}

@@

For the remainder, fix some $\rho$. We defined
\[
  q_t^*(\rho)
  =
  \argmin_{q \in \triangle_{N}}
  \sup_{p_t \in \triangle_{\mathcal D}'}
  \ex_{\hat\Delta_t\sim p_t}\left[
  q^\top \hat \Delta_t
    +
    \sum_{i=1}^N \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right],
  \]
  and so
  \begin{align*}
    &\lefteqn{\sup_{p_t\in\triangle_{\mathcal D}'}\sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ q_t^*(\rho)^\top \hat \Delta_t
    +
  \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right]}\\
    &=
      \inf_{q_t}
      \sup_{p_t\in\triangle_{\mathcal D}'}\sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ q_t^\top \hat \Delta_t
    +
  \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right].
\end{align*}
% Recall that this expression is an upper bound on 
% $  \sup_{j_t} \mathop{\ex}_{I_t\sim q_t}\left[ e_{I_t}^\top \hat \Delta_t(I_t,j_t,q_t)
%    + \rel(\hist^t)\right] -(t+1)N\gamma$.

@@

      \sup_{p_t\in\triangle_{\mathcal D}'}\sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ q_t^\top \hat \Delta_t

@@

    \sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ q_t^\top \hat \Delta_t

@@

    \sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ e_j^\top \hat \Delta_t

@@

    \inf_{j}  \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ e_j^\top \hat \Delta_t\right]

@@

Because $\pi$ is deterministic, we must have

@@

  \min_i \ex_{\hat\Delta_t \sim p_t}
  [e_i^\top\hat\Delta_t]

@@

  \ex_{\hat\Delta_t \sim p_t }[\pi(x_t)^\top\hat\Delta_t]

@@

    +\min_j \ex_{\hat\Delta_t'\sim p_t}\left[e_j^\top \hat\Delta_t'\right]

>>>>

\newpage
\bibliography{big_bib}

@@

  We now check the inductive step. We define $\rho = (x_t,\eepsilon_t,\Z_t)_{t+1:T}$ to the collection of random variables in the relaxation. Recall that our aim is to prove admissibility of the strategy $q_t(\rho) = (1-N\gamma)q_t^*(\rho)+ \gamma \ones$ where $q_t^*(\rho)$ was defined by
  \begin{align*}
  q_t^*(\rho)
  &=
  \argmin_{q \in \triangle_{N}}
  \sup_{p_t \in \triangle_{\mathcal D}'} 
    \exop_{\hat\Delta_t \sim p_t}\left[
    q^\top\hat\Delta_t
    +  \sum_{i=1}^N R_i\left(\hist^{t},\rho\right)
    \right]
    \\
    &=
      \argmin_{q \in \triangle_{N}}
  \sup_{p_t \in \triangle_{\mathcal D}'} 
    \sum_{i=1}^N
    \exop_{\hat\Delta_t \sim p_t}\left[
    q^\top\hat D_i\Delta_t
    +   R_i\left(\hist^{t},\rho\right)
    \right].
\end{align*}
By construction, no entry of $q_t(\rho)$ is below $\gamma$. It is then easy to check that, for $q_t^* = \ex_{\rho}[q_t^*(\rho)]$ and $q_t = \ex_{\rho}[q_t(\rho)]$,
\begin{align*}
  \ex_{I_t \sim q_t}\left[ e_{I_t}^\top \Delta_t \right] = q_t^\top \Delta_t^\top 
  \leq (q_t^*)^\top \Delta_t + N\gamma
  =
  \sum_{i=1}^N \ex_{I_t\sim q_t} \left[(q_t^*)^\top D_i \hat\Delta_t(I_t,j_t,q_t)^\top \right] + N\gamma,
\end{align*}
where we have been explicit that $\hat\Delta_t(I_t,j_t,q_t)$ is a random variable that depends on the player actions and the $q_t$ (since $\Z_t$'s distribution is a function of $q_t$).

For every fixed $x_t$, we can apply the above inequality and unpack the definition of the relaxation to find
\begin{align*}
  \sup_{j_t} \mathop{\ex}_{I_t\sim q_t}\left[e_{I_t}^\top\hat\Delta_t(I_t,j_t,q_t)
  +  \rel(\hist^t) \right]
  &=
    \sup_{j_t } \mathop{\ex}_{I_t\sim q_t}\left[e_{I_t}^\top\hat\Delta_t(I_t,j_t,q_t)
    +  \sum_{i=1}^N \exop_\rho\left[R_i\left(\hist^{t},\rho\right)\right]\right]\\
  &\quad + (T-t)N\gamma\\
  &\leq
    \sup_{j_t} \sum_{i=1}^N \mathop{\ex}_{I_t\sim q_t}\left[(q_t^*)^\top D_i \hat\Delta_t(I_t,j_t,q_t)
    +
  \exop_\rho\left[R_i\left(\hist^{t},\rho\right)\right]\right]\\
  &\quad+(T-t+1)N\gamma.
\end{align*}
Defining $A_i(\pi) = -\sum_{s=1}^{t-1} \pi(x_s)^\top D_i \hat \Delta_s - \sum_{s=t+1}^T 2\pi(x_s) \eepsilon_{s,i} \Z_{s}$, the previous line is equal to
\begin{align*}
\lefteqn{\sup_{j_t} \sum_{i=1}^N \mathop{\ex}_{I_t\sim q_t}\left[(q_t^*)^\top D_i \hat\Delta_t(I_t,j_t,q_t)
    +
  \mathop{\ex}_{\rho}\left[\sup_{\pi} - \pi(x_t)^\top \hat\Delta_t(I_t,j_t,q_t) + A_i(\pi)
  \right]\right] + (T-t+1)N\gamma}\\
  &\quad =
    \sup_{j_t} \sum_{i=1}^N\mathop{\ex}_{I_t\sim q_t}\left[\mathop{\ex}_{\rho}\left[ q_t^*(\rho)^\top D_i \hat \Delta_t (I_t,j_t,q_t)
    +
    \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t(I_t,j_t,q_t) + A_i(\pi)\right]\right]\\
  &\quad+ (T-t+1)N\gamma.
\end{align*}

@@

Specifically, every coordinate of $\hat\Delta_t(I_t,j_t,q_t)$  has large probability of being zero: if we fix $q_t$ by conditioning on $\rho$, then
\begin{align*}
  P\left(\hat\Delta_t(I_t,j_t,q_t)^\top e_i = 0 \right)
  &=
    \ex_{\rho}\left[ \ex_{I_t \sim q_t(\rho)}\left[ P\left(\hat\Delta_t(I_t,j_t,q_t)^\top e_i = 0 \middle |\rho, I_t\right)\right]\right]\\
    &=
    \ex_{\rho}\left[ \ex_{I_t \sim q_t(\rho)}\left[
    1-\frac{\gamma \vert e_i^\top V(I_t)^\top Y_t\vert }{V_\infty q_t(\rho)(I_t)}
    \right]\right]\\
  &\geq
    \ex_{\rho}\left[ \ex_{I_t \sim q_t(\rho)}\left[
    1-\frac{\gamma}{q_t(\rho)(I_t)}
    \right]\right]\\
  &= \ex_{\rho}\left[
    \sum_{i=1}^N q_t(\rho)(i) \left(1- \frac{\gamma}{q_t(\rho)(i)}\right)\right]\\
  &= 1 - N \gamma.
\end{align*}
Therefore, the distribution of $\hat\Delta_t(I_t,j_t,q_t)$ is always in $\triangle_{\mathcal D}'$, and we obtain an upper bound by allowing the adversary to play distributions over a random variable named $\hat\Delta_t$ with distribution in $\triangle_{\mathcal D}'$. With this substitution, $I_t$ and $j_t$ no longer appear in the expression. Suppressing the $(T-t+1)N\gamma$ term, we have
\begin{align*}
  &\lefteqn{
        \sup_{j_t } \sum_{i=1}^N\mathop{\ex}_{I_t\sim q_t}\left[\mathop{\ex}_{\rho}\left[ q_t^*(\rho)^\top D_i \hat \Delta_t(I_t,j_t,q_t)
    +
    \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t(I_t,j_t,q_t) + A_i(\pi)\right]\right]
    }\\
  &\leq
    \sup_{p_t\in\triangle_{\mathcal D}'} \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[
    \sum_{i=1}^N\mathop{\ex}_{\rho}\left[ q_t^*(\rho)^\top D_i \hat \Delta_t
    +
    \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right]\right]\\
    &\leq
\mathop{\ex}_{\rho}\left[ \sup_{p_t\in\triangle_{\mathcal D}'}\sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ q_t^*(\rho)^\top D_i \hat \Delta_t
    +
  \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right]\right].
\end{align*}

@@

For the remainder, fix some $\rho$. We defined
\[
  q_t^*(\rho)
  =
  \argmin_{q \in \triangle_{N}}
  \sup_{p_t \in \triangle_{\mathcal D}'}
  \ex_{\hat\Delta_t\sim p_t}\left[
  q^\top \hat \Delta_t
    +
    \sum_{i=1}^N \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right],
  \]
  and so
  \begin{align*}
    &\lefteqn{\sup_{p_t\in\triangle_{\mathcal D}'}\sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ q_t^*(\rho)^\top D_i \hat \Delta_t
    +
  \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right]}\\
    &=
      \inf_{q_t}
      \sup_{p_t\in\triangle_{\mathcal D}'}\sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ q_t^\top D_i \hat \Delta_t
    +
  \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right].
\end{align*}
% Recall that this expression is an upper bound on 
% $  \sup_{j_t} \mathop{\ex}_{I_t\sim q_t}\left[ e_{I_t}^\top \hat \Delta_t(I_t,j_t,q_t)
%    + \rel(\hist^t)\right] -(t+1)N\gamma$.

@@

      \sup_{p_t\in\triangle_{\mathcal D}'}\sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ q_t^\top D_i \hat \Delta_t

@@

    \sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ q_t^\top D_i \hat \Delta_t

@@

    \sum_{i=1}^N \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ e_j^\top D_i \hat \Delta_t

@@

    \inf_{j}  \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ e_j^\top D_i \hat \Delta_t\right]

@@

Because $\pi$ is deterministic, we must have, for all $i$,

@@

  \sum_{i=1}^N \min_j \ex_{\hat\Delta_t \sim p_t}
  [e_j^\top D_i \hat\Delta_t]
  =
  \min_j \ex_{\hat\Delta_t \sim p_t}
  [e_j^\top\hat\Delta_t]

@@

  \ex_{\hat\Delta_t \sim p_t }[\pi(x_t)^\top \hat\Delta_t]

@@

    +\min_j \ex_{\hat\Delta_t'\sim p_t}\left[e_j^\top D_i \hat\Delta_t'\right]
